Bird beak's elaboration and exploration: data preparation

### 2021-08-27 Analysis/01-Data_preparation.Rmd
final version for testing data

```{r}
## Make a dispRity object
shapespace <- custom.subsets(shapespace, group = all_groups)
formspace  <- custom.subsets(formspace, group = all_groups)
shape_axes <- select.axes(shapespace)
form_axes  <- select.axes(formspace)
```

@@

```{r}
## Save the data to be analysed in Data/Processed
form_shape_space_1tree_2levels <- list(
    "consensus_tree" = consensus_tree,
    "shape_space"    = shapespace,
    "form_space"     = formspace,
    "groups_list"    = all_groups)
save(form_shape_space_1tree_2levels, file = "../Data/Processed/form_shape_space_1tree_2levels.rda")
```

>>>>

```{r}
## Make a dispRity object and get axes data
shape_axes <- select.axes(custom.subsets(shapespace, group = all_groups))
form_axes  <- select.axes(custom.subsets(formspace, group = all_groups))
```

@@

```{r}
## Add the clade columns and the animal column to the spaces
shapespace <- as.data.frame(shapespace)
shapespace$level1 <- groups_level1$col
shapespace$level2 <- groups_level2$col
shapespace$animal <- rownames(shapespace)
formspace <- as.data.frame(formspace)
formspace$level1 <- groups_level1$col
formspace$level2 <- groups_level2$col
formspace$animal <- rownames(formspace)

## Save the data to be analysed in Data/Processed
form_shape_space_1tree_2levels <- list(
    "consensus_tree" = consensus_tree,
    "shape_space"    = shapespace,
    "shape_dim"      = shape_axes$dimensions,
    "form_space"     = formspace,
    "form_dim"       = form_axes$dimensions,
    "groups_list"    = all_groups)

save(form_shape_space_1tree_2levels, file = "../Data/Processed/form_shape_space_1tree_2levels.rda")
```
